---
title             : "Steven's Test Mansucript"
shorttitle        : "Test Manuscript"

author: 
  - name          : "Steven Mesquiti"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Princeton University, 
    Department of Psychology,
Peretsman Scully Hall,
Princeton, NJ 08540"
    email         : "sm9518@princeton.edu"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization, Data Collection, Data Analysis, Writing"


affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Princeton University"
authornote: |
  "This is my author note"

abstract: |
  Well-being comprises two distinct dimensions: subjective (pleasant life) and psychological (meaningful life), each with underlying components. Advances in natural language processing have enhanced automated assessment of psychological states and traits, allowing text-based assessments to capture subjective well-being with unprecedented accuracy. However, language's predictive ability for psychological well-being and its supporting components remains unstudied. This research investigates how effectively and for which facets of well-being we can predict from people's speech or writing. Across three studies, we examined the ability of language-based assessments to predict self-reported scores of psychological and subjective well-being components. Participants completed language-based assessments of life satisfaction and autonomy, along with self-reported measures of psychological and subjective well-being. We used contextual word embeddings generated from AI-based transformers to predict satisfaction with life and psychological well-being scores. Results showed that predicted scores from word embeddings of open-ended assessments correlated with out-of-sample scores (rs = 0.16-0.63) and generalized to other psychological well-being components (rs = 0.15-0.50), supporting the interconnected nature of well-being components in language use. However, we did not achieve the accuracy of previous studies (rs = 0.72-0.85), and autonomy was consistently less predictable than satisfaction with life. These findings provide emerging evidence that while psychological well-being is accessible through language, it may be more challenging to assess than subjective well-being.   
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "Upheavals, LIWC, Social Media, Reddit, Language"
wordcount         : "X words"

bibliography      : "/Users/sm9518/Downloads/Well-being-Prediction.bib"

floatsintext      : no
linenumbers       : no
draft             : Yes
mask              : no

figurelist        : Yes
tablelist         : Yes
footnotelist      : no

classoption       : "doc"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
if (!require("pacman")) install.packages("pacman") #run this if you don't have pacman 
library(pacman)
pacman::p_load(tidyverse, broom,papaja,tinytex,corrr,install = T) 
tinytex::install_tinytex(force = T)
r_refs("/Users/sm9518/Downloads/Well-being-Prediction.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r}
# load in the data from the google drive
data_dir = "/Users/sm9518/Library/CloudStorage/GoogleDrive-sm9518@princeton.edu/My Drive/Classes/PSY-503/Lab-5/data"

parents = read.csv(file.path(data_dir, "galton_child_parent_heights.csv"))

palette = c("#772e25", "#c44536", "#ee9b00", "#197278", "#283d3b", "#9CC5A1", "#6195C6", "#ADA7C9", "#4D4861", "grey50")
palette_condition = c("#ee9b00", "#c44536","#005f73", "#283d3b", "#9CC5A1", "#6195C6", "#ADA7C9", "#4D4861")
plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 8),
        text = element_text(size = 12, family = "Futura Medium"),
        axis.text = element_text(color = "black"),
        axis.ticks.y = element_blank())

```

# Class Assignment 

## Sample Text

# Predictive Validity of Language-Based Assessments of Well-being

## Introduction

In this report, I will examine the predictive validity of language-based assessments of well-being by comparing them to close-ended self-report measures of well-being in an online sample (N = 285). This dataset was collected during my role as a lab manager at Penn, and I will use it as a basis for an upcoming paper.

The analysis will employ transformer-based natural language processing and machine learning techniques, utilizing the R `text` package [@Kjell et al., 2022]. Specifically, I will generate word embeddings using Google’s `bert-large-uncased` model [@Devlin et al., 2019], which comprises 24 layers of 1024 dimensions each. Research has shown that the 23rd layer of BERT provides reliable results for document- and human-level predictions [@Devlin et al., 2019]; [@Ganesan et al., 2021]. I will use this layer to represent words and phrases as embeddings, which will then be applied in predictive models.

## Method

### Word Embedding Example

The following code demonstrates how embeddings are generated using the `textEmbed` function, specifying the second-to-last layer of BERT and concatenating token embeddings:

```
embeddings <- textEmbed(
  data = data[1:2], 
  model = "bert-large-uncased",
  layers = -2,  # Grabbing the second-to-last layer
  aggregation_from_layers_to_tokens = "concatenate",
  aggregation_from_tokens_to_texts = "mean",
  aggregation_from_tokens_to_word_types = "mean",
  keep_token_embeddings = TRUE
```


## Generating a Summary Table of the Parents Dataset

Below, we use `papaja` to generate a summary table of the parents dataset. As we can see, the mean parent height is `r round(mean(parents$parent_ht), 2)`, with a standard deviation of `r round(sd(parents$parent_ht), 2)`. The mean child height is `r round(mean(parents$child_ht), 2)`, with a standard deviation of `r round(sd(parents$child_ht), 2)`. Please see Table 1. 

### Table 1

```{r}
parents = parents %>%
  select(parent_ht, child_ht)

my_table <- t(apply(parents, 2, function(x) # Create data
  round(c(Mean = mean(x), SD = sd(x), Min = min(x), Max = max(x)), 2)
))


apa_table(
  my_table
  , align = c("l", rep("r", 3))
  , caption = "A summary table of the parents dataset."
)

```


# Methods

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis

We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Discussion

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
