---
title: "PSY 503: Lab 05 - Correlations, Regression with Dummy Coding"
author: "Steven Mesquiti"
date: "2024-10-08"
output: 
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document: yes
  word_document: yes
  github_document:
    toc: true
    toc_depth: 2
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# PSY 503: Lab 05 - Correlations, Regression with Dummy Coding
## Correlation and Regression
```{r}
if (!require("pacman")) install.packages("pacman") #run this if you don't have pacman 
library(pacman)
pacman::p_load(tidyverse, broom,corrr, patchwork, install = T) 

# load in the data from the google drive
data_dir = "/Users/sm9518/Library/CloudStorage/GoogleDrive-sm9518@princeton.edu/My Drive/Classes/PSY-503/Lab-5/data"

parents = read.csv(file.path(data_dir, "galton_child_parent_heights.csv"))

palette = c("#772e25", "#c44536", "#ee9b00", "#197278", "#283d3b", "#9CC5A1", "#6195C6", "#ADA7C9", "#4D4861", "grey50")
palette_condition = c("#ee9b00", "#c44536","#005f73", "#283d3b", "#9CC5A1", "#6195C6", "#ADA7C9", "#4D4861")
plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 8),
        text = element_text(size = 12, family = "Futura Medium"),
        axis.text = element_text(color = "black"),
        axis.ticks.y = element_blank())

```

Let's use the galton's child parent height data as before. CSV file here:
https://drive.google.com/file/d/1LK9jGBSpPr21S9_BzZhJi5Z68rB3JTEX/view?usp=sharing
Your tasks are to:
(1) Add two columns to the dataset: z_child_ht, and z_parent_ht which consists of
standardized heights scores for the two variables
```{r}

parents = parents %>%
  mutate(z_child_ht = scale(child_ht),
         z_parent_ht = scale(parent_ht))

parents |> 
  DT::datatable(rownames = FALSE, options = list(pageLength = 5)) 

```


(2) Install the package "corrr" if you don't have it already.
Use corrr::correlate() to compute the correlation matrix/ pair-wise correlations
for the variables in the data-frame. Display the matrix and save it within a new
dataframe. Explain the observed results.
You can also use cor() to get the correlation matrix, but corrr::correlate() works
better with tidyverse.

```{r warning=TRUE}

corrr::correlate(parents)

```

> Results show that parent height and child height are positively correlated. The correlation coefficient is 0.459, which is a moderate correlation. 


3) Create scatterplots of child_ht vs parent-ht, and z_child_ht vs z_parent_ht.
Add a linear regression line to the plot (it is fine to use geom_smooth).
Annotate the plot with the correlation value you had calculated earlier.
```{r}

parents |> 
  ggplot(aes(x = parent_ht, y = child_ht)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  labs(title = "Parent Height vs Child Height (raw data",
       x = "Parent Height",
       y = "Child Height") +
    annotate("text", x = max(parents$parent_ht), y = max(parents$child_ht),  
           label = "r = 0.45", color = "black", hjust = 1, vjust = 1, size = 5) + 
  plot_aes 

```

```{r}
parents |> 
  ggplot(aes(x = z_parent_ht, y = z_child_ht)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "purple") +
  labs(title = "Parent Height vs Child Height (Z-score)",
       x = "Parent Height",
       y = "Child Height") +
    annotate("text", x = max(parents$z_parent_ht), y = max(parents$z_child_ht),  
           label = "r = 0.45", color = "black", hjust = 1, vjust = 1, size = 5) + 
  plot_aes 
```

4)
(a) Fit a linear model to the data with
i) child_ht as the outcome variable, and parent_ht as the predictor/explanatory
variable.

```{r}
model_1 = lm(child_ht ~ parent_ht, data = parents)


model_1 |> summary()

```


ii) z_child_ht the outcome variable, and z_parent_ht as the predictor/explanatory
variable.
Save these results as new r objects.

```{r}
model_2 = lm(z_child_ht ~ z_parent_ht, data = parents)

model_2 |> 
  summary()
```


(b) Compare the co-efficients you observe for the two cases, and explain anything
salient about what you see.



> The first model has a coefficient of 0.646, while the second model has a coefficient of 0.459. The values are different because model 2 is using z-scored data. 

(c) Use glance() from the broom package to look at the several summary statistics
obtained for these regression fits. Explain anything salient about what you see
here.

```{r}

glance(model_1)
glance(model_2)
```

> The R-squared value for model 1 is 0.21, while the R-squared value for model 2 is 0.21. The R-squared values are the same because the models are principally the same. However, the different fit statistics for each model differ.

(d) We have come across the notion of total variance in the data, as well as
variance that is explained or unexplained by a model. Calculate these three values
for both set of models, and write about anything you find salient.
As a hint, all of these can be found with the var command.
The values you would be finding the variance of are either the (i) fitted data /
predictions, (ii) observed data, or (iii) model residuals.
You need to map these quantities to the different types of variance.
Feel free to use augment() from broom, or referencing obtaining these variables
from within the model object (lmfit_from_4a\$fitted, lmfit_from_4a\$resid)

Model 1 variance 

```{r}
# 1. Get fitted values (predictions), residuals, and observed data
fitted_values <- model_1$fitted.values  # Extract predicted values
residuals <- model_1$residuals  # Extract residuals
observed_values <- parents$child_ht # Replace with the actual column name for observed data

# 2. Calculate Total Variance (Observed Data)
Model_1_total_variance <- var(observed_values)

# 3. Calculate Explained Variance (Fitted Data / Predictions)
Model_1_explained_variance <- var(fitted_values)

# 4. Calculate Unexplained Variance (Residuals)
Model_1_unexplained_variance <- var(residuals)

# 5. Print the results
cat("Total Variance for Model 1:", Model_1_total_variance, 
    "\nExplained Variance for Model 1:", Model_1_explained_variance, 
    "\nUnexplained Variance for Model 1:", Model_1_unexplained_variance, "\n")
```

Model 2 Variance 

```{r}
# 1. Get fitted values (predictions), residuals, and observed data
fitted_values <- model_2$fitted.values  # Extract predicted values
residuals <- model_2$residuals  # Extract residuals
observed_values <- parents$z_child_ht # Replace with the actual column name for observed data

# 2. Calculate Total Variance (Observed Data)
Model_2_total_variance <- var(observed_values)

# 3. Calculate Explained Variance (Fitted Data / Predictions)
Model_2_explained_variance <- var(fitted_values)

# 4. Calculate Unexplained Variance (Residuals)
Model_2_unexplained_variance <- var(residuals)

# 5. Print the results
cat("Total Variance for Model 2:", Model_2_total_variance, 
    "\nExplained Variance for Model 2:", Model_2_explained_variance, 
    "\nUnexplained Variance for Model 2:", Model_2_unexplained_variance, "\n")


```

(e) Calculate explained variance/ total variance for both sets of models. Connect
results here with results from 4c and 2.

```{r}
cat("Model 1 Explained Variance / Total Variance:", Model_1_explained_variance / Model_1_total_variance, "\n",
    "Model 2 Explained Variance / Total Variance:", Model_2_explained_variance / Model_2_total_variance, "\n",
    "See, they're equal :)")

```

## Part 2. Regression Intro (Continuous outcome, categorical predictors)

Let's use the gapminder dataset that you have already worked with, and let's use
the most recent year of data.
To motivate our analysis, fundamental question in economic development is "How
does a country's geographic location relate to its economic prosperity?"
One interesting observation is that countries within the same continent often have
similar levels of economic development.
Do you guess differently about a country's economy knowing that it is in Africa or
that it is in Europe?
Well, in addition to guessing, we can look at the data and attempt a regression
analysis.
gdpPercap could be a proxy for economic prosperity
And we know the continents that each country belongs to.


```{r}

data <- gapminder::gapminder |> 
  filter(year == max(year)) 

data |> 
  filter(year == max(year)) |>
  DT::datatable(rownames = FALSE, options = list(pageLength = 20)) 
```
With regression, we can ask questions like:
1. Is there a difference in GDP per capita across continents?
2. How much of the variation in countries' GDP per capita can be explained by which
continent they're in?
and so on.

Step 1: Visualize data
```{r}


data |> 
ggplot(aes(x = gdpPercap)) +
geom_histogram(bins = 30, fill = "skyblue", color = "black") +
scale_x_continuous(labels = scales::dollar_format()) +
labs(title = "Distribution of GDP per capita",
x = "GDP per capita", y = "Count") +
  plot_aes
```
This data is right-skewed. It turns out that taking the log of per capita gdp in
such scenarios helps with skewness.
(It also helps economists talk more easily about rate of change of GDP and whether
that is increasing or not)
Let's transform the variable and observe the results
```{r}
# Let's use the most recent year of data
data = data |> 
mutate(log_gdp = log(gdpPercap))




# Visualize the distribution of GDP per capita
p1 <- ggplot(data, aes(x = gdpPercap)) +
geom_histogram(bins = 30, fill = "skyblue", color = "black") +
scale_x_continuous(labels = scales::dollar_format()) +
labs(title = "Distribution of GDP per capita",
x = "GDP per capita", y = "Count") +
theme(axis.text.x = element_text(angle = 45, hjust = 1)) +  # Rotate x-axis labels
plot_aes




# Visualize the distribution of log(GDP per capita)
p2 <- ggplot(data, aes(x = log_gdp)) +
geom_histogram(bins = 30, fill = "lightgreen", color = "black") +
labs(title = "Distribution of log(GDP per capita)",
x = "log(GDP per capita)", y = "Count") +
  plot_aes

p1 + p2
```
The transformed values seem more like a normal distribution and with less skew.
So let's uses log_gdp as our outcome variable.
Q5) Create dummy variables for the continent variable. Use the mutate() function to
add new columns, one for each continent except one (which will serve as the
reference category).
Use Africa as the reference category.
[Hint:
(1) "as.integer(continent == "Americas")" returns the value of 1 when the continent
is Americas, and 0 otherwise
(2) Note again, that you'll need one column less than all the possible continent
columns]
Show the first few rows of this new dataset.
```{r}

data_dummy = data |> 
  mutate(continent_America = as.integer(continent == "Americas"),
         continent_Asia = as.integer(continent == "Asia"),
         continent_Europe = as.integer(continent == "Europe"),
         continent_Oceania = as.integer(continent == "Oceania"))

data_dummy |> 
  DT::datatable()

```
Q6) Fit two models
Model A is the empty model that predicts log_gdp by only includes an intercept.
Model B is the model that predicts log_gdp based on continent.

```{r}
model_A = lm(log_gdp ~ 1, data = data_dummy)

model_A |> 
  summary()
```

```{r}
model_B = lm(log_gdp ~ continent, data = data_dummy)

model_B |> 
  summary()
```

Q7) Examine the results of the two models. What do you notice/ infer from it?
Try using glance() for this model too, and elaborate on what you think is salient.

```{r}
glance(model_A)
```
```{r}
glance(model_B)
```

> I notice that R squared, signame, and AIC values are different for each model. For model B the 


Q8) Create a strip plot of log_gdp for each continent, with a box plot overlaid.
This will show both the individual country data points and the overall distribution
for each continent. Use ggplot2 to create this visualization. Does this visual
support the conclusions you drew from the R-squared value?
[Hint: Strip plots are generated by using geom_jitter();
Given that you are overlaying the boxplot over the strip-plot, use the alpha
parameter to ensure that the boxplot is not opaque and obscuring the datapoints.
For the boxplot, set outlier.shape = NA, so that outliers are not plotted --- we
already have the data visualized including outliers]


```{r}
ggplot(data, aes(x = continent, y = log_gdp)) +
  geom_jitter(alpha = 0.6, width = 0.2, color = "blue") +  # Strip plot with jitter
  geom_boxplot(outlier.shape = NA, alpha = 0.4, fill = "skyblue") +  # Boxplot without outliers
  labs(title = "Log GDP by Continent",
       x = "Continent",
       y = "Log GDP") +
  plot_aes

```
