---
title: "PSY-503: Lab 2"
author: "Steven Mequiti"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document: default
  word_document: default
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.path = "lab_2_plots/")
options(scipen=999)
set.seed(123)
```

# Lab 2 {.tabset}

# Set-up Tasks {.tabset}

## Install and Load Packages

```{r load-packages}
if (!require("pacman")) install.packages("pacman") #run this if you don't have pacman 
library(pacman)
pacman::p_load(tidyverse, tinytex,ggdist,gghalves,knitr,install = T) 
```

## Task with YAML Header (A)

-   Edit the YAML header / metadata to reflect your name.
-   Title should say *Steven Mesquiti* and today's date: `r Sys.Date()`

## Task with Markdown and R chunks {.tabset}

### Write Formula for Variance

$$variance for sample = \frac{\sum (x_i - \bar{x})^2}{n - 1}$$

$$variance for population = \frac{\sum (x_i - \bar{x})^2}{n}$$ \### Compute SS for provided vectors

```{r}
compute_SS <- function(x) {
  n <- length(x)
  mean_x <- mean(x)
  sum_squared_diff <- sum((x - mean_x)^2)
  return(sum_squared_diff)
}

vector_a <- c(5, 5, 5, 5, 5)
vector_b <- c(1, 3, 5, 7, 9)

print(paste("Sum of squares for vector a:", compute_SS(vector_a)))
print(paste("Sum of squares for vector b:", compute_SS(vector_b)))

```

## Descriptives (dplyr) and Visualization tasks {.tabset}

```{r load datasauRs}
library(datasauRus)
lab2_datasaurus<- datasaurus_dozen

#define plot aesthetic
plot_aes = theme_minimal() +
  theme(legend.position = "bottom",
        text = element_text(family = "Futura Medium"),
        axis.ticks.y = element_blank(),
        plot.title = element_text(hjust = 0.5, vjust = 1.5),
        plot.caption = element_text(hjust = 1, size = 10),
        legend.text = element_text(size = 7, family = "Futura Medium")  # Adjust legend text here
  )

```

In the previous lab, we worked with a data from DataSaurus. We visualized y against x for different values of the column named *"dataset"*. Now, carry out this visualization but with the following changes.

### Show all the different visualizations within a single graph using *facets* in ggplot

```{r fig.height=8, fig.width=8}
ggplot(lab2_datasaurus, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset) +
  plot_aes
```

### Create grey-scale plots

```{r fig.height=8, fig.width=8}
ggplot(lab2_datasaurus, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset) +
  plot_aes +
  scale_colour_grey() ### adding grey-scale after we use the aesthetic object to override the colors
```

### Change the shape of the plotted points based on the condition

```{r fig.height=8, fig.width=8}
ggplot(lab2_datasaurus, aes(x = x, y = y, color = dataset, shape = dataset)) + 
  geom_point() +
  facet_wrap(~dataset) +
  plot_aes + 
  scale_shape_manual(values = c(0:13)) +  # Specify more shapes manually
  scale_colour_grey()
```

### Create a boxplot for each dataset

```{r}
ggplot(lab2_datasaurus, aes(x = dataset, y = x, color = dataset)) +
  geom_boxplot() +
  geom_half_violin(side = "l", alpha = 0.5) +  
  geom_jitter(width = 0.2, height = 0, alpha = 0.2) +  # Adding jitter with some transparency
  plot_aes


```

You've learned that looking at the data is important. But summary statistics can be useful too. The following dplyr-based code computes the mean of `lab2_datasaurus` for each dataset within it, for the variable x and stores it into a new dataframe.

## Summary stats Dataframes

```{r}
summary_stats <- lab2_datasaurus %>%
  summarise(
    mean_x = mean(x, na.rm = TRUE),
    mean_y = mean(y, na.rm = TRUE),
    median_x = median(x, na.rm = TRUE),
    median_y = median(y, na.rm = TRUE),
    variance_x = var(x, na.rm = TRUE),
    variance_y = var(y, na.rm = TRUE),
    correlation_xy = cor(x, y, use = "complete.obs")
  )

# Print the dataframe using kable
kable(summary_stats, caption = "Summary Statistics for x and y")

```

## Observations

> Based on the summary stats, the mean and median values for x and y are similar across the different datasets. However, y has way more variance than X. Further, the two variables are not correlated.

## Combining two sources of data in a graph

> The red circle represents the means

```{r fig.height=8, fig.width=8}
ggplot(lab2_datasaurus, aes(x = x, y = y, color = dataset)) + 
  geom_point() +
  facet_wrap(~dataset) +
  geom_point(aes(x = mean(x), y = mean(y)), size = 5, shape = 1, color = "red", alpha = 0.5) +  # Overlaying the mean of x and y
  plot_aes 

```

## RMD vs. Quarto

> that the produced visuals are much more interactive than with R-markdown

## Tasks with YAML Header (B)

> displayinng code for the new header... 

```         
---
title: "PSY-503: Lab 2"
author: "Steven Mequiti"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document: default
  word_document: default
  github_document:
    toc: true
    toc_depth: 2
---
```

## Extracting the code back to r

```{r}
knitr::purl("Lab-2.Rmd")
```

`{r} knitr::purl("Lab-2.Rmd")`

## End of lab.

:) 
