---
title: "PSY-503: Lab 1"
author: "Steven Mequiti"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE,fig.path = "lab1_plots/")
options(scipen=999)
```

# Lab 1 {.tabset}

## Install and load the following packages

> Use pacman to load in the packages nicely

```{r load packages, message=FALSE, include=T}
if (!require("pacman")) install.packages("pacman") #run this if you don't have pacman 
library(pacman)
pacman::p_load(coursekata,tidyverse,datasauRus, install = T) 
```

## Display the overall structure of this dataframe

```{r}
# Load the data

df = datasaurus_dozen

str(df)
head(datasaurus_dozen,10)
```

> This dataset is in long format and has different x and y coordinates for various aspects of shapes. Dataset is a nominal variable and x and y are continuous variables

## Printing unique dataset values

```{r}
print(unique(df$dataset))
```

> What's being printed are the unique nominal values that are present in the `dataset` column

## Select a subset of lab1_data which has the value of "dataset" equal to "circle", and save it in a new variable temp_data

> use `temp_data = df %>% filter(dataset == "circle")` to complete this

```{r}
temp_data = df %>% 
  filter(dataset == "circle")

```

## Create Scatterplot of X and Y for the Circle data

```{r circle-plot}

plot_aes = theme_minimal() +
  theme(legend.position = "none",
        text = element_text(family = "Futura Medium"),
        axis.ticks.y = element_blank(),
        plot.title = element_text(hjust = 0.5, vjust = 1.5),
        plot.caption = element_text(hjust = 1, size = 10),
        legend.text = element_text(size = 7, family = "Futura Medium")  # Adjust legend text here
  )
gf_plot(temp_data, x = ~ x, y = ~ y) %>%
  gf_point( color = 'blue') + plot_aes
```

## Make a dino

```{r dino-plot}
df %>% 
  filter(dataset == "dino") %>% 
  gf_plot(x = ~ x, y = ~ y) %>%
  gf_point(color = 'dodgerblue2')

```

## Make a star

```{r star-plot}
df %>% 
  filter(dataset == "star") %>% 
  gf_plot(x = ~ x, y = ~ y) %>%
  gf_point(color = 'orange')

```
