---
title: "PSY-503: Lab 3"
author: "Steven Mequiti"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document: yes
  word_document: yes
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.path = "lab_3_plots/")
options(scipen=999)
set.seed(123)
```

# Lab 2 {.tabset}

# Set-up Tasks {.tabset}

## Install and Load Packages

```{r load-packages}
if (!require("pacman")) install.packages("pacman") #run this if you don't have pacman 
library(pacman)
pacman::p_load(tidyverse,tinytex,ggdist,gghalves,knitr,gapminder,install = T) 

palette = c("#772e25", "#c44536", "#ee9b00", "#197278", "#283d3b", "#9CC5A1", "#6195C6", "#ADA7C9", "#4D4861", "grey50")
palette_condition = c("#ee9b00", "#c44536","#005f73", "#283d3b", "#9CC5A1", "#6195C6", "#ADA7C9", "#4D4861")
plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 8),
        text = element_text(size = 12, family = "Futura Medium"),
        axis.text = element_text(color = "black"),
        axis.ticks.y = element_blank())
```

# Lab 3 - Gapminder Data Wrangling Lab Assignment

Using the Gapminder dataset, complete the following tasks. Use tidyverse and dplyr functions and pipes where appropriate.
Remember to load the necessary libraries and the Gapminder dataset before starting.

```{r}
data = gapminder

data %>% 
  head() %>% 
  DT::datatable()
```


## 1) Find all countries in Asia with a life expectancy greater than 75 years in 2007.
```{r}
data %>% 
  filter(year == 2007 & continent == "Asia" & lifeExp > 75) %>% 
  select(country, lifeExp) %>% 
  DT::datatable()
```

## 2) List the top 5 countries with the highest GDP per capita in 2007, in descending order.
```{r}
data %>%
  filter(year == 2007) %>%
  arrange(desc(gdpPercap)) %>%   # Use arrange() to sort in descending order
  head(5) %>% 
  DT::datatable()
```

## 3) Create a new dataframe with only the country, continent, and GDP per capita for the year 2007.
```{r}
data %>% 
  filter(year == 2007) %>% 
  select(country, continent, gdpPercap) %>% 
  DT::datatable()

```

## 4) Add a new column called "gdp" that calculates the total GDP (GDP per capita * population) for each country in 2007.\
```{r}
data %>% 
  filter(year == 2007) %>% 
  mutate(gdp = gdpPercap * pop) %>% 
  select(country, gdpPercap, gdp, pop) %>%
  DT::datatable()
```

## 5) Create two separate dataframes: one for countries in Europe and one for countries in Africa, both for the year 2007. Then bind these dataframes together.
```{r}
europe_2007 <- data %>%
  filter(year == 2007, continent == "Europe") 

africa_2007 <- data %>%
  filter(year == 2007, continent == "Africa") 

europe_africa_2007 <- bind_rows(europe_2007, africa_2007)

# View the combined dataframe
europe_africa_2007 %>% 
  DT::datatable()
```

## 6) Calculate the average life expectancy and total population for each continent in 2007.
```{r}
data %>% 
  filter(year == 2007) %>% 
  group_by(continent) %>% 
  summarise(avg_lifeExp = mean(lifeExp), total_pop = sum(pop)) %>% 
  DT::datatable()
```

## 7) Create a wide format dataframe that shows the population for each country across all life expectancies as columns.

```{r}
data %>% 
  select(year,country, pop) %>% 
  pivot_wider(names_from = country, 
              values_from = pop,
              names_prefix = "Population_") %>%  # Replace spread with pivot_wider
  DT::datatable()
```
